An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-18 paper.tex
Subject table is simpler, closes #83 and #96.
- Got rid of self-reported mass column and replaced the NA's in the Measured
  Mass column with the self-reported mass. Noted this in the caption of the
  table. issue #83
- Added a mkdir to the subject table so that you can run it first in a fresh
  repo with no issues. issue #96

\section*{Methods}
\subsection*{Participants}
%
Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The study was approved by the Institutional Review
Board of Cleveland State University (\# 29904-VAN-HS) and written informed
consent was obtained from all participants. The data has been anonymized with
respect to the participants' identities and a unique identification number was
assigned to each subject. A selection of the meta data collected for each
subject is shown in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. The measured mass is computed from the mean total vertical ground
    reaction force just after the calibration pose event, if possible.
    Additional trials found in the data set with a subject identification
    number 0 are trials with no subject, i.e.  unloaded trials that can be used
    for inertial compensation purposes, and are not shown in the table. Generated
    by \verb|src/subject_table.py|.}
  \centering
  \small
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}

@@

\section*{Acknowledgments}
%
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.
We also thank Sabrina Abram, Brad Humphreys, and Anne Koelewijn for reviewing
the preprint and being our guinea pigs on the software/data instructions. Dan
Simon also gave valuable feedback on the preprint.

>>>>

\section*{Methods}
\subsection*{Participants}
%
Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The study was approved by the Institutional Review
Board of Cleveland State University (\# 29904-VAN-HS) and written informed
consent was obtained from all participants. The data has been anonymized with
respect to the participants' identities and a unique identification number was
assigned to each subject. A selection of the meta data collected for each
subject is shown in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns provide the trial numbers associated with each nominal treadmill
    speed. The measured mass is computed from the mean total vertical ground
    reaction force just after the calibration pose event, if possible. If the
    mass is reported without an accompanying standard deviation, it is the
    subject's self-reported mass. Additional trials found in the data set with
    a subject identification number 0 are trials with no subject, i.e.
    unloaded trials that can be used for inertial compensation purposes, and
    are not shown in the table. Generated
    by \verb|src/subject_table.py|.}
  \centering
  \small
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}

@@

\section*{Acknowledgments}
We thank Roman Boychuk and Obinna Nwanna for assistance with the experiments.
